Ornaments as indicators of social change before and after European arrival at Kiwulan, Northeastern Taiwan

### 2019-08-27 analysis/paper/paper.Rmd
typo

```{r plot-all-densities, fig.cap= "Kernal density map for ornaments by periods. Used the bandwidth based on Silverman(1986)'s rule of thumb."}
# apply function to each data frame in the list
titles <- names(ornaments_period_join_cen)
png(
  here("analysis", "figures",
       "plot-kde-maps.png"), 
    width = 190,
    height = 63,
    units = "mm",
  res = 300)
par(mfrow = c(1, 3),
    oma = c(1,1,1,1) + 0.1,
    mar = c(0,0,1,1) + 0.1)
kernels_for_plotting <- 
  map2(ornaments_period_join_cen, 
       titles,
      ~density_analysis(.x, main = .y))
invisible(dev.off())
knitr::include_graphics(here("analysis", 
                             "figures", 
                             "plot-kde-maps.png"))
```

>>>>

```{r plot-all-densities, fig.cap= "Kernal density map for ornaments by periods. Used the bandwidth based on Silverman (1986)'s rule of thumb."}
# apply function to each data frame in the list
titles <- names(ornaments_period_join_cen)
png(
  here("analysis", "figures",
       "plot-kde-maps.png"), 
    width = 190,
    height = 63,
    units = "mm",
  res = 300)
par(mfrow = c(1, 3),
    oma = c(1,1,1,1) + 0.1,
    mar = c(0,0,1,1) + 0.1)
kernels_for_plotting <- 
  map2(ornaments_period_join_cen, 
       titles,
      ~density_analysis(.x, main = .y))
invisible(dev.off())
knitr::include_graphics(here("analysis", 
                             "figures", 
                             "plot-kde-maps.png"))
```
